On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-08 main.tex
Update main.tex
Some typos corrected
Update main.tex
More typos

For $i$ in $\{1,\dots,n\}$ and $f$ as above, we will let $\I(i, f)$
denote the sequence of $n-(i-1)$ polynomials $(f, {\pa f}/{\pa
  X_{i+1}},\dots,{\pa f}/{\pa X_n})$. As pointed out in the
introduction, their zero-set is the $i$th polar variety
$W(\pi_i,V(f))$.  Then, we say that $f$ satisfies $\textbf{H}_i$ if
\begin{enumerate}
\item For any $\xb$ in $W(\pi_i,V(f))$, the Jacobian matrix
  $\jac_\Xb(\I(i, f))$ has full rank $n-(i-1)$ at $\xb$.

  {\em By the Jacobian Criterion~\cite[Corollary 16.20]{ECA}, this
  implies that $W(\pi_i,V(f))$ is either empty or $(i-1)$-equidimensional,
  and that $\I(i, f^\mA)$ is radical.}

@@

Let $\bm\Psi: \C^n \times \C^{i-1} \rightarrow \C^{n}$ be the mapping defined by the polynomials
\[
  (X_1-S_1,\hdots,X_{i-1}-S_{i-1}, f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n} ).
\]
%
\begin{lemma}
  $\bz$ is a regular value of $\bm\Psi.$
\end{lemma}
\begin{proof}
At all $(\xb,\bm\sigma)$ zeros of $\bm\Psi,$ the Jacobian matrix of
$\bm\Psi$ has full rank $n$. Indeed, indexing columns 
by $X_1,\dots,X_n,S_1,\dots,S_{i-1}$, this matrix is equal to
\[
\left[ 
\begin{array}{cc}
\bI_{i-1}\hspace{7mm} \bz_{(i-1)\times (n-i+1)}&\hspace{-10mm}-\bI_{i-1}\\
\jac_{\xb}\left(f,\frac{\pa
  f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\right)&\bz_{(n-i+1)\times (i-1)}
\end{array}
\right].
\] 
Since the Jacobian of $f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa
  f}{\pa X_n}$ at $\xb$ is non-zero (by $\textbf{H}_i$), the entire
matrix must have full rank $n$. Thus,  $\bz$ is a regular value of $\bm\Phi.$
\end{proof}

@@

Consider again the $n\times n$ matrix of indeterminates
$\A=(\A_{j,k})_{1 \le j,k \le n}$ and the field $\C(\A)$,
and define $f^{\A} \in \C(\A)[X_1,\dots,X_n]$.  Since $i$ is fixed, to
simplify notation, let $\I^\A$ denote the following polynomials in
$\C(\A)[X_1,\dots,X_n]$:
$$\I(\pi_i,f^\A)= \big (f^\A, {\pa f^\A}/{\pa X_{i+1}},\dots,{\pa
  f^\A}/{\pa X_n}) \big ),$$ and let $W^\A$ denote their zero-set,
that is, $W(\pi_i,V(f^\A)).$ In Section~\ref{ssec:Hi1}, we saw that
$f^\A$ satisfies $\textbf{H}_i(1)$, so that $\I^\A$ defines a
radical ideal, and $W^\A$ is equidimensional of dimension $i-1$. We
now point out that $f^\A$ also satisfies $\textbf{H}_i(2)$.

@@

Now, by construction of
\[
S := \{1,2,\hdots,\lceil 3\epsilon^{-1}6n^3(2d)^{2n}\rceil \}
\] 
and 
\[
T := \{1,2,\hdots,\lceil 3\epsilon^{-1}nd^{2n} \rceil \},
\] 
where $\mA \in S^{n^2}$ and  $\bm \sigma \in T^{n-1}$ are randomly chosen, we have 
%
\[
\pr[\Delta(\mA)=0] \leq  \frac{\deg\Delta}{|S|} = \epsilon/3
\]
and
\[
\pr[\Xi(\bm \sigma)=0] \leq \deg \frac{\deg\Xi}{|T|} = \epsilon/3.
\]
%
Let $\mathscr{E}$ be the event that the parametrizations
$[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$ returned in step 6 of
Algorithm~1 are correct. Then, the probability of success is equal to
\begin{align*}
 \pr[\Delta(\mA)\ne 0] \times \pr[\Xi(\bm \sigma)\ne 0 ~|~\Delta(\mA) \ne 0] \times \pr[\mathscr{E}~|~
   \Delta(\mA)\Xi(\bm\sigma) \ne 0].
\end{align*}
%
Set $k = \lg(3n/\epsilon)$ so that 
\[
(1-2^{-k})^n = (1 - \epsilon/(3n))^n \geq 1 - \epsilon/3,
\]
by Bernoulli's inequality. Therefore, 
\begin{align*}
\pr[\textrm{success}] &\geq (1- \epsilon/3)(1-
\epsilon/3)\pr[\mathscr{E}~|~   \Delta(\mA)\Xi(\bm\sigma) \ne 0]\\ 
& \geq (1- \epsilon/3)(1-
\epsilon/3)(1-2^{-k})^n \\ & \geq (1- \epsilon/3)(1- \epsilon/3)(1-
\epsilon/3)\\ & \geq 1 - \epsilon.
\end{align*}
This finishes the proof our main theorem.

>>>>

For $i$ in $\{1,\dots,n\}$ and $f$ as above, we will let $\I(i, f)$
denote the sequence of $n-(i-1)$ polynomials $(f, {\pa f}/{\pa
  X_{i+1}},\dots,{\pa f}/{\pa X_n})$. As pointed out in the
introduction, their zero-set is the $i$-th polar variety
$W(\pi_i,V(f))$.  Then, we say that $f$ satisfies $\textbf{H}_i$ if
\begin{enumerate}
\item For any $\xb$ in $W(\pi_i,V(f))$, the Jacobian matrix
  $\jac_\Xb(\I(i, f))$ has full rank $n-(i-1)$ at $\xb$.

  {\em By the Jacobian Criterion~\cite[Corollary 16.20]{ECA}, this
  implies that $W(\pi_i,V(f))$ is either empty or $(i-1)$-equidimensional,
  and that $\I(i, f)$ is radical.}

@@

Let $\bm\Psi: \C^n \times \C^{i-1} \rightarrow \C^{n}$ be the mapping defined by the polynomials
\[
  (X_1-S_1,\hdots,X_{i-1}-S_{i-1}, f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n} ).
\]
%
\begin{lemma}
  $\bz$ is a regular value of $\bm\Psi.$
\end{lemma}
\begin{proof}
At all zeros $(\xb,\bm\sigma)$ of $\bm\Psi,$ the Jacobian matrix of
$\bm\Psi$ has full rank $n$. Indeed, indexing columns 
by $X_1,\dots,X_n,S_1,\dots,S_{i-1}$, this matrix is equal to
\[
\left[ 
\begin{array}{cc}
\bI_{i-1}\hspace{7mm} \bz_{(i-1)\times (n-i+1)}&\hspace{-10mm}-\bI_{i-1}\\
\jac_{\xb}\left(f,\frac{\pa
  f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}\right)&\bz_{(n-i+1)\times (i-1)}
\end{array}
\right].
\] 
Since the Jacobian of $f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa
  f}{\pa X_n}$ at $\xb$ is non-zero (by $\textbf{H}_i$), the entire
matrix must have full rank $n$. Thus,  $\bz$ is a regular value of $\bm\Phi.$
\end{proof}

@@

Consider again the $n\times n$ matrix of indeterminates
$\A=(\A_{j,k})_{1 \le j,k \le n}$ and the field $\C(\A)$,
and define $f^{\A} \in \C(\A)[X_1,\dots,X_n]$.  Since $i$ is fixed, to
simplify notation, let $\I^\A$ denote the following polynomials in
$\C(\A)[X_1,\dots,X_n]$:
$$\I(i,f^\A)= \big (f^\A, {\pa f^\A}/{\pa X_{i+1}},\dots,{\pa
  f^\A}/{\pa X_n}) \big ),$$ and let $W^\A$ denote their zero-set,
that is, $W(\pi_i,V(f^\A)).$ In Section~\ref{ssec:Hi1}, we saw that
$f^\A$ satisfies $\textbf{H}_i(1)$, so that $\I^\A$ defines a
radical ideal, and $W^\A$ is equidimensional of dimension $i-1$. We
now point out that $f^\A$ also satisfies $\textbf{H}_i(2)$.

@@

Now, by construction of
\[
S := \{1,2,\hdots,\lceil 3\epsilon^{-1}6n^3(2d)^{2n}\rceil \}
\] 
and 
\[
T := \{1,2,\hdots,\lceil 3\epsilon^{-1}nd^{2n} \rceil \},
\] 
where $\mA \in S^{n^2}$ and  $\bm \sigma \in T^{n-1}$ are randomly chosen, we have 
%
\[
\pr[\Delta(\mA)=0] \leq  \frac{\deg\Delta}{|S|} = \epsilon/3
\]
and
\[
\pr[\Xi(\bm \sigma)=0] \leq  \frac{\deg\Xi}{|T|} = \epsilon/3.
\]
%
Let $\mathscr{E}$ be the event that the parametrizations
$[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$ returned in step 6 of
Algorithm~1 are correct. Then, the probability of success is equal to
\begin{align*}
 \pr[\Delta(\mA)\ne 0] \times \pr[\Xi(\bm \sigma)\ne 0 ~|~\Delta(\mA) \ne 0] \times \pr[\mathscr{E}~|~
   \Delta(\mA)\Xi(\bm\sigma) \ne 0].
\end{align*}
%
Set $k = \lg(3n/\epsilon)$ so that 
\[
(1-2^{-k})^n = (1 - \epsilon/(3n))^n \geq 1 - \epsilon/3,
\]
by Bernoulli's inequality. Therefore, 
\begin{align*}
\pr[\textrm{success}] &\geq (1- \epsilon/3)(1-
\epsilon/3)\pr[\mathscr{E}~|~   \Delta(\mA)\Xi(\bm\sigma) \ne 0]\\ 
& \geq (1- \epsilon/3)(1-
\epsilon/3)(1-2^{-k})^n \\ & \geq (1- \epsilon/3)(1- \epsilon/3)(1-
\epsilon/3)\\ & \geq 1 - \epsilon.
\end{align*}
This finishes the proof of our main theorem.
